---
title: "CCIWR main analysis"
author: "Felix Zaussinger and Johann Schuur"
date: "02.06.2020"
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    number_sections: true
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, results='asis')
options(digits=4)

knitr::opts_chunk$set()

# remove all objects from R workspace
rm(list=ls())

# Load necessary packages
library(broom)
library(estimatr)
library(gsynth)
library(haven)
library(MASS)
library(texreg)
library(margins)
library(tidyverse)
library(pander)
library(bookdown)
library(sandwich)
library(ggeffects)
library(AER)
library(reshape2)
library(corrplot)
library(readxl) # read xls and xlsx files
library(tidyr)
library(ncdf4)
library(chron)

# set plotting theme
theme_set(theme_classic())

# set working directory (Felix)
setwd("~/ETH/code/cciwr")

# set working directory (Johann)
#setwd("~/cciwr/")
```

```{r, include=FALSE}
# Note:
# ------
# Figures are referenced by simply referring to the name of the code block: _(figure \@ref(fig:A))_.
# Figure panels can be created by adding _..., fig.show = 'hold', out.width = '50%'_ to the curly brackets of the code block.
# Example: {r blockname, fig.cap="figure capture", fig.show = 'hold', out.width = '50%'}

# output table
#htmlreg(list(m1, m2), 
#        custom.model.names = c('m1', 'm2),
#        caption="", label="tab:", center = FALSE, star.symbol = "\\*")
```


## Data {-}
Monte Carlo simulation data
```{r}
df <- read.csv(file="data/monte_carlo/")
```

Read GRUN data
```{r}
# open netCDF file
grun <- nc_open("./data/GRUN/GRUN_discharge_cropped_small_tigris.nc")

lat <- ncvar_get(grun, "X")
lon <- ncvar_get(grun, "Y")
time <- ncvar_get(grun, "time")
tunits <- ncatt_get(grun,"time","units")
runoff <- ncvar_get(grun, "Runoff") # mm/day

# convert time -- split the time units string into fields
from <- strsplit(tunits$value, " ")
tstamps <- as.Date(time, origin=unlist(from)[3])

# mosul time series location
# Mosul: lat = 36.32, lon = 43.15
# Bagdad: lat = 33.30, lon = 44.38

read_grun <- function(lat_point, lon_point) {
  lat_idx <- which.min(abs(lat - lat_point)) # X
  lon_idx <- which.min(abs(lon - lon_point)) # Y
  grun_data <- (runoff[lat_idx, lon_idx,])
  df_grun <- data.frame(date = tstamps, runoff = grun_data)
  return(df_grun)
}

# combine to data frame
df_grun <- read_grun(36.32, 43.15)

# grun_ilisu
grun_ilisu <- read_grun(37.530112, 41.851024)

merged = data.frame(date=tstamps, mosul = df_grun$runoff, ilisu = grun_ilisu$runoff)
write.csv(merged, "grun_data.csv")

```

Read Dahiti altimetry data
```{r}
# read csv file
dahiti <- read.table("./data/Dahiti_dgfi_tum_altimetry/dahiti.dgfi.tum.de.txt")

# open netCDF file
dahiti_nc <- nc_open("./data/Dahiti_dgfi_tum_altimetry/118_water_level_altimetry.nc")
```

Summary
```{r}
besiri <- as.data.frame(tidy(summary(station_data_besiri$discharge_obs)))
mosul <- as.data.frame(tidy(summary(station_data_mosul$discharge_obs))[,1:6])
bagdad <- as.data.frame(tidy(summary(station_data_bagdad$discharge_obs))[,1:6])

row.names(besiri) <- "Besiri"
row.names(mosul) <- "Mosul"
row.names(bagdad) <- "Bagdad"

rbind(besiri, mosul, bagdad)
```

Time series plot
```{r fig.width=10, fig.height=5}
# Discharge plot
ggplot() + 
  geom_line(aes(x=date, y=discharge_obs, color="Besiri"), data = station_data_besiri) + 
  geom_line(aes(x=date, y=discharge_obs, color="Mosul"), data = station_data_mosul) + 
  geom_line(aes(x=date, y=discharge_obs, color="Bagdad"), data = station_data_bagdad) +
  labs(title="GRDC discharge", y="Discharge (m^3/s)")
```

normalise with z-score
```{r}
df_grun$runoff_norm <- (df_grun$runoff - mean(df_grun$runoff, na.rm = TRUE)) / sd(df_grun$runoff, na.rm = TRUE)

station_data_besiri$discharge_obs_norm <- (station_data_besiri$discharge_obs - mean(station_data_besiri$discharge_obs, na.rm = TRUE)) / sd(station_data_besiri$discharge_obs, na.rm = TRUE)

station_data_mosul$discharge_obs_norm <- (station_data_mosul$discharge_obs - mean(station_data_mosul$discharge_obs, na.rm = TRUE)) / sd(station_data_mosul$discharge_obs, na.rm = TRUE)

station_data_bagdad$discharge_obs_norm <- (station_data_bagdad$discharge_obs - mean(station_data_bagdad$discharge_obs, na.rm = TRUE)) / sd(station_data_bagdad$discharge_obs, na.rm = TRUE)
```

GRUN runoff in mm/day
```{r fig.width=10, fig.height=5}
ggplot() +
  geom_line(aes(x=date, y=runoff_norm, color="GRUN at Mosul"), data = df_grun) + 
  geom_line(aes(x=date, y=discharge_obs_norm, color="Besiri"), data = station_data_besiri) + 
  geom_line(aes(x=date, y=discharge_obs_norm, color="Mosul"), data = station_data_mosul) +
  geom_line(aes(x=date, y=discharge_obs_norm, color="Bagdad"), data = station_data_bagdad) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  labs(title="Normalised discharge (z-scored)", y="sd")
```

TUM Dahiti water level data Mosul dam in m
```{r}
# Altimetry time series plot
dahiti$V1 <- as.Date(dahiti$V1, '%Y-%m-%d')

ggplot() +
  geom_line(aes(x = V1, y = V2, colour = "Mosul dam"), data = dahiti) +
  # add minimal water level required in Mosul dam
  #geom_hline(yintercept = 300, linetype = "dashed") +
  geom_vline(xintercept = as.numeric(as.Date("2019-06-01")), linetype = "dashed") +
  labs(x = "Date", y = "Water level", title = "Altimetry of the Mosul dam between 1992 and present")
```

Violinplot
```{r}
ggplot() + 
  geom_violin(aes(x='Besiri', y=discharge_obs_norm, color="Besiri"), data = station_data_besiri) + 
  geom_violin(aes(x='Mosul', y=discharge_obs_norm, color="Mosul"), data = station_data_mosul) + 
  geom_violin(aes(x='Bagdad', y=discharge_obs_norm, color="Bagdad"), data = station_data_bagdad) + 
  geom_violin(aes(x='GRUN Bagdad', y=runoff, color="GRUN Bagdad"), data = df_grun) + 
  labs(title="GRDC discharge", y="Discharge (m^3/s)")
  #geom_line(aes(x=date, y=discharge_obs, color="Besiri"), data = station_data_besiri) + 
  #geom_line(aes(x=date, y=discharge_obs, color="Mosul"), data = station_data_mosul) + 
  #geom_line(aes(x=date, y=discharge_obs, color="Bagdad"), data = station_data_bagdad) +
```

Correlation p(GRUN at bagdad, station at bagdad)
```{r}
df_merged <- merge(df_grun, station_data_mosul, by="date")

tidy(cor.test(df_merged$runoff_norm, df_merged$discharge_obs_norm))
```

corr altimetry 
```{r}
altimetry_mosul <- data.frame(date=dahiti$V1, water_level = dahiti$V2)

df_merged2 <- merge(df_grun, altimetry_mosul, by="date")

tidy(cor.test(df_merged2$runoff, df_merged2$water_level))
```

Based on an article is likely that the filling of Ilisu started June 10th. Source: https://www.reuters.com/article/us-turkey-dam-erdogan-idUSKCN1QO1V5
```{r}
ols <- lm(runoff ~ water_level, df_merged2)
tidy(summary(ols))

beta0 = as.numeric(coef(ols)[1])
beta1 = as.numeric(coef(ols)[2])

altimetry_mosul$discharge_prediction <- beta0 + beta1 * altimetry_mosul$water_level

ggplot() +
  geom_line(aes(x = date, y = discharge_prediction, colour = "Mosul dam"), data = altimetry_mosul) +
  # add minimal water level required in Mosul dam
  #geom_hline(yintercept = 300, linetype = "dashed") +
  geom_vline(xintercept = as.numeric(as.Date("2019-06-10")), linetype = "dashed") +
  labs(x = "Date", y = "Discharge (mm/day)", title = "Approximate runoff based on regression with altimetry data")
```

repeat for ilisu
```{r}
df_merged_ilisu <- merge(grun_ilisu, altimetry_mosul, by="date")
tidy(cor.test(df_merged_ilisu$runoff, df_merged_ilisu$water_level))

ols_ilisu <- lm(runoff ~ water_level, df_merged_ilisu)
tidy(summary(ols_ilisu))

beta0 = as.numeric(coef(ols_ilisu)[1])
beta1 = as.numeric(coef(ols_ilisu)[2])

altimetry_mosul$discharge_prediction_ilisu <- beta0 + beta1 * altimetry_mosul$water_level

```

plot resulting ts for ilisu and mosul

```{r}
ggplot() +
  geom_line(aes(x = date, y = runoff, colour = "GRUN Ilisu"), data = grun_ilisu %>% filter(date > 2000)) +
  geom_line(aes(x = date, y = discharge_prediction, colour = "Mosul dam"), data = altimetry_mosul) +
  geom_line(aes(x = date, y = discharge_prediction_ilisu, colour = "Ilisu dam"), data = altimetry_mosul) +
  
  # add minimal water level required in Mosul dam
  #geom_hline(yintercept = 300, linetype = "dashed") +
  geom_vline(xintercept = as.numeric(as.Date("2019-06-10")), linetype = "dashed") +
  labs(x = "Date", y = "Discharge (mm/day)", title = "Approximate runoff based on regression with altimetry data")
```
```{r}
grun_ilisu
```

